MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
Table 13 and 14 added

###Plot Result
  The explanation from the plot above are as follows:   
  1. Defender distance range from 0 to 2 feet, the accuracy varied between 42% to 50%  
  2. Defender distance range from 2 to 4 feet, the accuracy rate for this distance range from 44% to 49%  
  3. Defender distance range from 4 to 6 feet, the accuracy rate for this distance range from 41% to 46%
  4. Defender distance range from 6 to 8 feet, the accuracy rate for this distance range from 37% to 42%
  5. Defender distance range from 8 to 10 feet, the accuracy rate for this distance range from 37% to 54%
  6. Defender distance more than 10 feet up until 16 feet, the accuracy varies greater than previous distance range, starting from 33% to 60%.  
  7. Distance greater than 16 feet, the data varies between 0% (no shots scored from that distance) to 100% (certain successfull shot from that distance)

@@

**Table 13**: The relationship between the shooter distance ranges and accuracy

  Distance (in feet) | Accuracy (range in %)
  - | -
  0 - 2 | 62 - 68
  2 - 4 | 61 - 67
  4 - 6 | 44 - 58
  6 - 8 | 38 - 51
  8 - 10 | 35 - 42
  10 - 12 | 34 - 42
  12 - 14 | 37 - 47
  14 - 16 | 33 - 51
  16 - 18 | 37 - 48
  18 - 24 | 33 - 43
  24 - 28 | 18 - 38
  28+ | 0 - 50

>>>>

###Plot Result
  The explanation from the plot above is summerised in the following table:

** Table 13**: Relationship between the defender distance and accuracy

Defender Distance (range in feet) | accuracy (range in %) 
- | -
0 - 2 | 42 - 50
2 - 4 | 44 - 49
4 - 6 | 41 - 46
6 - 8 | 37 - 42
8 - 10 | 37 - 54
10 - 16 | 33 - 60
16+ | 0 - 100

@@

**Table 14**: Relationship between the shooter distance ranges and accuracy

  Shooter Distance (in feet) | Accuracy (range in %)
  - | -
  0 - 2 | 62 - 68
  2 - 4 | 61 - 67
  4 - 6 | 44 - 58
  6 - 8 | 38 - 51
  8 - 10 | 35 - 42
  10 - 12 | 34 - 42
  12 - 14 | 37 - 47
  14 - 16 | 33 - 51
  16 - 18 | 37 - 48
  18 - 24 | 33 - 43
  24 - 28 | 18 - 38
  28+ | 0 - 50
